Consistent, and weak, ecosystem functional response across precipitation extremes in a sagebrush steppe

### 2017-08-23 manuscript/usses_water_ms.tex

\title{Consistent ecosystem functional response across precipitation extremes
in a sagebrush steppe}

@@

\textbf{Discussion.} Despite some evidence that ecosystem functional
response saturated under extreme wet conditions, the response of ANPP to
soil moisture and community compositional changes in this sagebrush
steppe system were consistently small. The similarity, or difference, of
ecosystem functional response across treatments was not due to
compensatory shifts at the plant community level, but instead reflects
the weak responses of individual species. Such responses may be due to
bet-hedging strategies where species respond weakly to even extreme
levels of soil moisture to ensure low variance of long-term success.
% Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text.
\end{abstract}

@@

The results of our five year experiment in a sagebrush steppe conform to
two of our four predictions, depending on treatment. Under chronic
drought, neither ecosystem functional response nor community composition
changed (Fig. 1, top left). But under irrigation, ecosystem functional
response was different from the control treatment while community
composition remained unchanged (Fig. 1, top right). Thus, we found some
evidence for a saturating response at high water availability (Fig. 3),
but the response of ANPP to soil moisture was weak overall, regardless
of treatment (Table 1).

>>>>

\title{Consistent, and weak, ecosystem functional response across precipitation
extremes in a sagebrush steppe}

@@

\textbf{Discussion.} Despite some evidence that ecosystem functional
response saturated under extreme wet conditions, the response of ANPP to
soil moisture was consistintly weak and community composition was
remarkably stable. The similarity, or difference, of ecosystem
functional response across treatments was not due to compensatory shifts
at the plant community level, but instead reflects the weak responses of
individual species. Such responses may be due to bet-hedging strategies
where species respond weakly to even extreme levels of soil moisture to
ensure low variance of long-term success.
% Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text.
\end{abstract}

@@

The results of our five year experiment in a sagebrush steppe conform to
two of our four predictions, depending on treatment. Under chronic
drought, neither ecosystem functional response nor community composition
changed (Fig. 1, top left). But under irrigation, ecosystem functional
response was different from the control treatment while community
composition remained unchanged (Fig. 1, top right). Thus, we found some
evidence for a saturating response at high water availability (Fig. 3A,
right panel). However, the response of ANPP to soil moisture was
consitently weak, regardless of treatment (Table 1).
